%-------------------------
% Resume in Latex
% Author: Jake Gutierrez
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\usepackage{contour}
\usepackage{ulem}

\setlength{\footskip}{5pt}

% --- yoinked from https://alexwlchan.net/2017/latex-underlines/
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% \usepackage{datatool, filecontents}
% \DTLsetseparator{,}
% \DTLloaddb[noheader, keys={thekey,thevalue}]{confidential}{data/confidential.dat}
% \newcommand{\var}[1]{\DTLfetch{confidential}{thekey}{#1}{thevalue}}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeDegree}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeDegreePartTwo}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Cooper Ellidge} \\ \vspace{1pt}
  \small \faPhone[solid] \hspace{1pt} \small \href{tel:+61 458 781 380}{\myuline{0458 781 380}} $|$
  \small \faEnvelope[solid] \hspace{1pt} \small \href{mailto:cooper.ellidge@gmail.com}{\myuline{cooper.ellidge@gmail.com}} $|$
  % \small \faUser[solid] \hspace{1pt} \href{https://cooperellidge.github.io}{\myuline{cooperellidge.github.io}} $|$
  \small \faGithub \hspace{1pt} \small \href{https://github.com/cooperellidge}{\myuline{github.com/cooperellidge}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{iO Energy}{}
{Software Engineer}{Sep 2023 -- Now}
\resumeItemListStart
\resumeItem{Developed features for an internal energy retail sales platform, improving customer growth from 1000 to over 2000 customers and reducing sales agent errors, using React, Javascript, AWS, Python, and Flask.}
\resumeItem{Forecasted electricity demand and financial profit using Python, pandas, and FB Prophet.}
\resumeItem{Created microservices for handling customer signups, plan management, and sales commissions.}
\resumeItem{Developed a full-stack app to calculate and reconcile financial contracts with AEMO market settlements.}
\resumeItem{Used Snowflake data warehouse to integrate ETL pipelines into BI and risk management dashboards.}
\resumeItem{Designed and architected a new energy retail SaaS product using Django, React, Typescript, and Docker.}
\resumeItemListEnd

\resumeSubheading
{Saab Australia}{}
{Software Engineer}{Jan 2023 -- Aug 2023}
\resumeItemListStart
\resumeItem{Designed, developed, integrated and tested modules for 9LV Combat Management System using Java, Vue, Typescript, and DDS in an MVVM software architecture.}
\resumeItem{Presented new software capability to RAN customers during contract milestone demonstrations.}
\resumeItemListEnd

\resumeSubSubheading
{Early Careers Lead}{Sep 2022 -- Aug 2023}
\resumeItemListStart
\resumeItem{Coordinated over 50 graduates and interns for Saab's Early Careers Programs, including developing the programs' strategic direction, determining rotations, providing mentorship, and organising events.}
\resumeItem{Created an optimisation algorithm for team assignment, balancing business needs with graduate preferences.}
\resumeItemListEnd

\resumeSubSubheading
{Graduate Engineer}{Jan 2021 -- Dec 2022}
\resumeItemListStart
\resumeItem{Using full-stack software engineering skills to deliver naval operator user interfaces and enhanced tactical capabilities for RAN's surface fleet.}
\resumeItem{Created an internal Python package to model and analyse autonomous vehicle's algorithm performance.}
\resumeItem{Conducted requirements analysis and designed hospital modules for Defence's deployable hospital (JP2060), receiving a company award nomination for critical effort in producing major contract deliverables.}
\resumeItem{Designed mechanical components for the Swedish submarine program in collaboration with our Swedish colleagues.}
\resumeItemListEnd

\resumeSubSubheading
{Undergraduate Engineer}{Nov 2019 -- Feb 2020}
\resumeItemListStart
\resumeItem{Prototyped and evaluated deep learning models using Python to improve environmental measurements using sensor data. The capability has since been successfully tested during sea trials.}
\resumeItemListEnd


\resumeSubheading
{Centre for the Subatomic Structure of Matter, University of Adelaide}{}
{Physics Summer Research Student}{Jan 2019 -- Feb 2019}
\resumeItemListStart
\resumeItem{Modelled experimental results for theoretical dark matter particles using a cloud supercomputer.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Wedding Site} $|$ \textit{React, Python, Material UI, AWS, Terraform}}{}
\resumeItemListStart
\resumeItem{Created a site for my wedding, including passcode protection, RSVPs, notifications, and Google Maps integration.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Resume Repo} $|$ \small \faGithub \hspace{1pt} \href{https://github.com/cooperellidge/resume}{\myuline{github.com/cooperellidge/resume}} $|$ \textit{LaTeX, GitHub Actions}}{}
\resumeItemListStart
\resumeItem{Built a repo that compiles a resume (this one!) to PDF using GH Actions and deploys it to GH Pages.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeDegree
{University of Adelaide}{}
{Bachelor of Engineering (Mechanical)(Honours) with}{Feb 2016 -- Nov 2020}
\resumeDegreePartTwo
{Bachelor of Science (Mathematics and Theoretical Physics)}{GPA 6.7/7.0}
\resumeSubHeadingListEnd


%
%-----------SKILLS-----------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
        \textbf{Languages}{:
          Python,
          JavaScript,
          TypeScript,
          Java,
          SQL,
          HTML,
          CSS
          % Fortran
        } \\
        \textbf{Tools and libraries}{:
          %-----------JS frameworks
          React,
          Vue,
          % Next.js,
          % HTMX,
          %-----------Cloud, infra, CI/CD
          AWS,
          % Vercel,
          Terraform,
          Docker,
          Jenkins,
          %-----------Python frameworks
          FastAPI,
          Django,
          % Chalice,
          Streamlit,
          %-----------Scientific stack
          pandas,
          NumPy,
          SciPy,
          % Matplotlib,
          % Plotly,
          %-----------AI/ML + data
          keras,
          % scikit-learn,
          FB Prophet,
          Snowflake,
          Dagster,
          DBT,
          %-----------General programming tools
          Git,
          GitHub,
          Jira,
          BitBucket,
          Confluence,
          % FeCru,
          Notion
          % Figma
        } \\
        \textbf{Software}{:
          Creo Parametric,
          %-----------Modelling/simulation
          MATLAB,
          Simulink,
          ANSYS suite,
          % COMSOL Multiphysics,
          %-----------CAD
          AutoDesk Inventor,
          SolidWorks,
          %-----------Systems Engineering
          DOORS,
          Windchill,
          IFS,
          %-----------Modelling/simulation
          Microsoft Office suite
        } \\
        }}
\end{itemize}

%-------------------------------------------
\end{document}